---
name: Alexander Robertson-Jones
position: "BSc Marine Biology"
address: "School of Energy, Geoscience, Infrastructure and Society | Heriot-Watt University"
phone: +447879400435
www: 
email: "alexrobertson.jones@gmail.com"
twitter:
github: 
linkedin: 
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

***********

## **About Me**
 * PADI Dive Master, scientific diving contractor and underwater photography experiance.
 * First class BSc Hons Marine Biology.
 * Temperate and tropical biogenic reef restoration experience.
 * Experiance Driving 4X4s and towing medium sized loads.
 * Profficient in R and general computing (made this CV using the "vitae" R package).
 
I have just completed my degree in marine biology and am eager to get back into the world of research and conservation. I have had the opportunity to take
part in scientific diving work in both temperate and tropical waters and I am keen to continue my skill
development in this area. Most of my work and own research has focused on habitat restoration of biogenic reefs. 
I also have wider interests in technology and computing solutions used in the marine biology industry and believe that it is a great time for people with the right skills and vison to develop novel cost-effective solutions to conservation issues.  

I am a stikler for details but also realise there is a time and a place for just getting things working to get the job done. I enjoy working with and learning from others but I also work well on my own. 

## **Relevant Work and Accademic History**  


**St Abbs marine station, 30th Jul 2018 – 7th Sep 2018 (volunteer)**[*-website link*](http://marinestation.co.uk/#)  

 **Duties:** General maintenance of aquariums, setting up and taking apart tanks for new arivals. Raising European lobster larvae. Conducting shore surveys of juvenile brown crab _Cancer pagurus_. Assisting in the design and construction of experements

**Herriot watt university scientific dive team, 5th Dec 2018 -Present (paid)**[*-website link*](https://hwscientificdivers.wordpress.com/)  

 **Duties:** Deployment of European flat oysters in the Dornoch firth for a reef restoration project. Survey and sample collection dives in Loch Creran. Collecting deep sediment cores. Video transects and drift surveys of *Limaria hians* and *serpula vermicularis* biogenic reefs.

**Biosecurity for DEEP project- Sep 2018, present (paid)**[*-website link*](http://www.theglenmorangiecompany.com/about-us/deep/)  

 **Duties:** Cleaning oysters of epifauna and maintaining them in lab-based aquaria. Developing new protoclos designed to improve the scalability of the project. Communicating our research to journalists and funders was also a key part of the job. I was also involved in transporting the oysters. I have also attended the 2019 NORA (Native Oyster Restoration Alliance) conferance and university open days as out reach for the project. 
 
**NORA (Native Oyster Restoration Alliance) conferance staff** 19th May 2019 - 24th May (paid)[*-website link*](https://noraeurope.eu/)  
  
 **Duties:** I assisted in the planning and logistices  the 2019 NORA (Native Oyster Restoration Alliance) conferance and university open days as out reach for the project. I was part of the team in charge of registering attendees and asisting the chairs of sessions. We also ran an excursion at the end of the last day of the conferance where we presented oyster related history information at several relevent locations in the area. Social media was another task i assisted with, curating photos from the photographer and working with other staff to showcase the conferance, mostly on twitter. I learened a lot about running such an event and thouroughly enjoyed the chance to meet people and see talks.
 

  **Tengah island conservation, 28th May 2018 - 24th Jul 2018 (volunteer)**[*-website link*](https://www.batubatu.com.my/tengah-island-conservation)  
  

 **Duties:** lead surveys of reef fish and invertebrates. Turtle nest patrols (by foot and boat) and
collecting eggs for the hatchery. Turtle necropsies and nest excavations to determine stage of
development of un-hatched eggs. Communicating the importance of our research and
conservation work to guests of the resort. Leading beach clean-ups with guests. Relocating
snakes and centipedes away from inhabited areas. We were also responsible for constructing
and maintaining a tree nursery (developed a methodology for cultivating mangroves). One of the most rewarding parts of my time at Tengah island conservation was finding species that were previously unknown on the island and identifying some of the common residents which had not yet been identified.

##**Education**  

**BSc Marine Biology**  

    Honours Project 6th Sept - 29th Feb 
    
  Grade 78%
My dissertation focussed on the restoration of *Limaria hians* biogenic reefs on the west coast of scotland. It involved surveys of wild reefs in Port Appin and laboritory based experiments to inform restoration attempts. Work in port appin further supported previous work showwing a continued decline in the reef. Lab based work included the development of a programmable camera system to record long time lapses of behaviour under infrared light over multiple days. The lab experements also included substrate prefferance experements to see where disturbed *L. hians* specimens would preferentialy settle.  

    Grades  
  
  Classification - 1st class

4th year grade average |3rd year grade average – 76% |
2nd year grade average – 79% |
1st year grade average – 70% 

##**Other Work History (Further Details Avalible on request)**

Deliveroo bike courier, Oct 2018 – present  

Kitchen porter at “steak” restaurant, July 31st 2017 – August 28th 2017  

Cashier at Chinese restaurant, September 2014 – September 2015  

Reptile husbandry, UK exotics, September 2011 – September 2015

```{r}
#kable(Job_history_table[1:4,])
```


##**Personal Inerests** 

From an early age I have been facinated by the ocean spending much of my childhood freediving on the south coast of england. I am now a keen SCUBA diver and would dive every day if my finanicial, and physiological limits would alow me! Climbing is another pass time I enjoy and i love to be outdoors. I am also an amateur photographer venturing into the world of underwater photography. I believe photography is an essential part of communicating conservation and research to the public and its a skill I enjoy developing. In my spare time I enjoy tinkering with various things, I have repaired several vintage game consoles and am self-taught in programming (Python and R). I also enjoy working on all things mechanical, cars, bikes etc. Plants are another interest of mine and I grow all sorts on the windowsill in my flat.

In the near future I hope to progress my diving futher by completing trimix and advanced nitrox training. I also hope to complete my powerboat liscense as although i do have boat handeling experiance I currently do not have anything on paper.

